Active Learning : From Blackbox To Timed Connectors

### 2016-01-08 paper/paper.tex
.

Besides, we're going to add a single ``T'' action in mealy machines. It indicates that a transition
will take a time unit to finish, and all outputs would come out after that.

\subsection{Parameterized Mealy Machine}
We present a model named \emph{parameterized mealy machine} to represent timed connectors
(hereinafter referred to as PMM). This
model is supposed to behave as a middle representation. Connectors are defined as parameterized
mealy machines, and composed via its production operator. Then original mealy-machine model will be
taken as semantics of PMM model.

@@

\section{From Blackbox to Timed Connectors}
\subsection{Adapted L* Algorithm}
\subsection{Equivalence Query}
Generally, equivalence query has been proved impossible in blackbox
models\cite{DBLP:journals/iandc/Angluin87}. However, in this
section, we're showing that in certain circumstances, equivalence query can be implemented with
no approximation.

>>>>

Besides, we're going to add a ``T'' action in mealy machines. It indicates that a transition
will take a time unit to finish, and all outputs would come out after that.

\subsection{Parameterized Mealy Machine}
We present a model named \emph{parameterized mealy machine} to represent timed connectors
(hereinafter referred to as PMM).

This model is supposed to behave as a middle representation. Connectors are defined as parameterized
mealy machines, and composed via its production operator. Then original mealy-machine model will be
taken as semantics of PMM model.

@@

\section{From Blackbox to Timed Connectors}

\subsection{Observation Table}

\subsection{Closeness}

\subsection{Perfomance Optimization}

\subsection{Counter-Examples}
Generally, equivalence query has been proved impossible in blackbox
models\cite{DBLP:journals/iandc/Angluin87}. However, in this
section, we're showing that in certain circumstances, equivalence query can be implemented with
no approximation.
